### 2023-05-27 paper.tex
new version

% meia risca meio traço alt+0150
% heat transfer rate through radiation
% o core tem termometro do veículo que é separado. A luz aquece o sheeem (baixa capacidade termica) e é determinada a temperatura

\documentclass[portuguese]{cenarticle}
%----------------------------------------------------------------------------------------
%	PUBLISH INFO (not for authors)
%----------------------------------------------------------------------------------------
%
\issn{2179-460X}
%
\volume{44}
%
\eJournal{eXX}
%
\doi{https://doi.org/10.5902/2179460Xxxxxx}
%
\submitionDate{xx/xx/xx}
%
\approvalDate{xx/xx/xx}
%
\publishDate{xx/xx/xx}
%
\yearonfooter{xxxx}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
\usepackage{pgfplots}
\usepackage{graphicx}

@@

\usepackage{booktabs}
\usepackage{multirow}
%
%----------------------------------------------------------------------------------------
%	YOUR CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\sisetup{math-micro=\text{µ},text-micro=µ}
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
\renewcommand{\thefigure}{\arabic{figure}}
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data Collection and Analysis}
%
\portugueseTitle{Explorando a Dinâmica dos Raios e seus Efeitos Térmicos: Insights a partir da Coleta e Análise de Dados}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

\shortHeaderTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data ...}
\shortHeaderAuthors{Babbage{\it~et~al.}}
%
\portugueseAbstract{
Os relâmpagos, um fenômeno natural poderoso, não só despertam nossa curiosidade, mas também têm um impacto significativo no ambiente circundante. Este estudo tem como objetivo investigar a dinâmica dos relâmpagos e seus efeitos térmicos por meio de uma análise abrangente de dados coletados pelo Electroplumbus Nimbodetector, em conjunto com o veículo voador 14-Bis. A configuração experimental oferece uma plataforma única para a coleta de dados em tempo real dentro de tempestades de raios, permitindo a exploração dos processos intricados associados às descargas de raios e aos fenômenos térmicos resultantes. A correlação entre a intensidade dos raios e a transferência de radiação térmica é examinada por meio de uma série de experimentos de campo e medições. Os resultados revelam uma relação significativa, com um aumento na energia transferida por radiação correspondendo a raios de maior intensidade. Ao estudar as transições atômicas subjacentes dentro do detector, são obtidos insights sobre a conversão da energia dos relâmpagos em calor no ar circundante. Essas descobertas contribuem para nossa compreensão dos fenômenos térmicos induzidos por relâmpagos e lançam as bases para pesquisas adicionais em ciências atmosféricas, meteorologia e estudos ambientais. As implicações deste estudo se estendem a medidas de segurança aprimoradas, ciência climática e conhecimento aprofundado da dinâmica atmosférica.
}
%
\portugueseKeywords{raio, radioatividade, experimento aéreo, tempestade}
%
\englishAbstract{
Lightning, a powerful natural phenomenon, not only captivates our curiosity but also significantly impacts the surrounding environment. This study aims to investigate the dynamics of lightning and its thermal effects through a comprehensive analysis of data collected by the Electroplumbus Nimbodetector, in conjunction with the 14-Bis flying vehicle. The experimental setup provides a unique platform for real-time data collection within lightning storms, allowing for the exploration of the intricate processes associated with lightning discharges and the resulting thermal phenomena. The correlation between the intensity of lightning strikes and the transfer of thermal radiation is examined through a series of field experiments and measurements. The results reveal a significant relationship, with an increase in the energy transferred by radiation corresponding to higher intensity lightning strikes. By studying the underlying atomic transitions within the detector, insights into the conversion of lightning energy into heat in the surrounding air are gained. These findings contribute to our understanding of lightning-induced thermal phenomena and lay the foundation for further research in atmospheric science, meteorology, and environmental studies. The implications of this study extend to improved safety measures, climate science, and enhanced knowledge of atmospheric dynamics.
}
%
\englishKeywords{Lightning; Radioactivity; Airborne experiment; Storm}
%
%----------------------------------------------------------------------------------------
\begin{document}

@@

\section{Introduction}
%
Lightning, a powerful natural phenomenon, has long fascinated scientists and researchers due to its immense energy and unpredictable behavior. The study of lightning and its effects on the surrounding environment is crucial for gaining a deeper understanding of atmospheric dynamics and improving safety measures against its potential hazards. In particular, the transfer of thermal radiation during lightning strikes plays a significant role in shaping the thermal characteristics of the atmosphere and has far-reaching implications for meteorology, climate science, and environmental studies.\par
%
To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required. In this paper, we present the results of a comprehensive study conducted using the 14-Bis flying vehicle and the Electroplumbus Nimbodetector, designed specifically for data collection within lightning storms. These innovative instruments enable researchers to gather valuable insights into the intricate processes associated with lightning discharges and the resulting thermal phenomena.\par
%
In the following sections, we present the experimental setup, data collection methods, and data analysis techniques employed in this study. Subsequently, we discuss the results obtained, highlighting the correlation between lightning strikes and the transfer of thermal radiation. Finally, we conclude with a summary of the findings, their significance, and future research directions.\par
%
\section{Experimental Setup}
\subsection{The 14-Bis flying vehicle}
The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms. The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions.\par
%
Its streamlined shape is optimized for aerodynamic efficiency, minimizing drag and turbulence to facilitate smooth movement through the air. The veicle incorporates pairs of rigid horizontal structures projecting from both sides, designed to provide stability and support during flight \citep{Wipo}, enabling the driver to maintain control even in the presence of strong winds and atmospheric disturbances.\par
%
Within the open cockpit, the driver securely straps into a harness, ready to embark on their mission into lightning storms. The propulsion system powered by the kerosene motor generates the necessary thrust for controlled ascent \citep{Torrens1992}, while the open design ensures an immersive experience for the driver, allowing them to observe and collect data in real-time.\par
%
With its purpose-driven design and reliable motor, the 14-Bis flying vehicle represents an instrumental tool for conducting data collection within lightning storms. The combination of an open cockpit, sturdy structural elements, and efficient propulsion system allows for precise maneuverability and enables researchers to gather valuable insights into the dynamics of these atmospheric phenomena.
%
\begin{figure}[!h]
  \caption{The 14-bis flying vehicle}
  \vspace{-3mm} 
  \begin{center}
    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
  \end{center}
  {\footnotesize
  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}.\\
  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons.}
    \label{fig:triangle2}
  \end{figure}

@@

  The 4th generation Electroplumbus Nimbodetector is a specialized device designed to collect data from a sensor and measure thermal radiation during lightning strikes. The device incorporates a modified version of the Plumbus Combobulator in its core, along with a specially engineered sensor that has a prism shape and is filled with an enriched Glowing Schleem substance. The purpose of the device is to gather data on lightning discharges and study their effects on the surrounding air.\par
  %
  The sensor within the Electroplumbus Nimbodetector is designed to capture thermal radiation emitted during lightning strikes. When a lightning event occurs, the Glowing Schleem inside the prism-shaped sensor heats up. Due to the low heat capacity of the Schleem, the temperature rise is rapidly measured, providing instant data on the thermal effects of the lightning discharge.\par
  %
  To determine the temperature of the air surrounding the sensor, the Plumbus Combobulator within the device incorporates a conventional thermometer with hight heat capaciity. The thermometer is strategically strategically positioned on the rear of the 14-bis flying vehicle to measure the air temperature in the vicinity of the sensor. By comparing the temperature of the Schleem-filled sensor and the air temperature measured by the thermometer, we can establish the temperature difference, which is crucial in assessing the impact of the lightning strikes' radiation on the surrounding air.\par
  %
  The Electroplumbus Nimbodetector undergoes rigorous calibration and validation processes to ensure accurate and reliable measurements. Prior to deployment, the device is calibrated against reference instruments and tested under controlled laboratory conditions to establish its performance characteristics. Special attention is given to the sensitivity, precision, and response time of the sensor and thermometer to ensure the accurate capture of data during lightning strikes.
  %
  \begin{figure}[!h]
    \newcommand\x{0.25}
    \caption{The 4th generation of the Electroplumbus Nimbodetector}
    \begin{center}
      \vspace{-3mm}
      \begin{minipage}[t]{\x\linewidth}
        \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
        \captionsetup{justification=centering, font=footnotesize}
        \caption*{(a)}\label{fig:triangle2a}
      \end{minipage}
      \begin{minipage}[t]{\x\linewidth}
        \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
        \captionsetup{justification=centering, font=footnotesize}
        \caption*{(b)}\label{fig:triangle2b}
      \end{minipage}\\
    \end{center}%
    \vspace{-1mm}
    {\footnotesize
    Source: Craiyon website, see \citep{Craiyon}\\
    Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance\\
    }
    \label{fig:triangle2}
    \end{figure}\vspace{-4mm}
  %
  \subsection{Data Collection}

@@

\section{Results}

@@

The chart presents the number of lightning strikes detected by the Nimbus Detector within different altitude ranges. As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.

The chart presented in Figure 1 illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation. As the intensity of the lightning strike increases, there is a clear upward trend in the energy transferred. This observation supports the hypothesis that lightning strikes contribute to an enhanced transfer of thermal radiation to the surrounding air.

The strong correlation observed between lightning strikes and the energy transferred by radiation reinforces the reliability of the data collected by the Electroplumbus Nimbodetector. These findings provide valuable insights into the thermal dynamics associated with lightning discharges and contribute to a better understanding of the effects of lightning on the surrounding environment.

Moreover, it is important to note that light alone cannot directly heat gas molecules. Instead, during a lightning strike, the light emitted excites the electrons in atoms within the detector. These atoms are already vibrating at a certain frequency. Some of these atoms vibrate with sufficient vigor that their vibrational energy matches the electronic energy (photons) absorbed from the lightning, effectively reaching resonance with the solar energy. As a result, these atoms undergo a quantum transition from being "electronically excited" to "vibrationally excited," causing the entire atom to move. The surrounding air perceives this excited vibration as "heat."

This mechanism provides a deeper understanding of how the energy from a lightning strike is converted into thermal energy in the air. By studying the vibrational and electronic transitions occurring within the atoms of the detector, we can further elucidate the intricate processes involved in the thermal effects of lightning discharges.

In conclusion, this study demonstrates a strong correlation between the intensity of lightning strikes and the transfer of thermal radiation. The data collected by the Electroplumbus Nimbodetector, along with the presented chart, provides robust evidence supporting this relationship. Additionally, the exploration of the underlying processes involving electronic and vibrational transitions within the detector atoms enhances our comprehension of how lightning energy is converted into heat in the surrounding air. These findings contribute to the scientific understanding of lightning-induced thermal phenomena and lay the foundation for future research in this field.

@@

  {\setlength{\parindent}{0pt}
    \input{authorshipAndContributions.tex}
  }

>>>>

\documentclass[english]{cenarticle}
%----------------------------------------------------------------------------------------
%	PUBLISH INFO (not for authors)
%----------------------------------------------------------------------------------------
%
\issn{2179-460X}
%
\volume{44}
%
\eJournal{eXX}
%
\doi{https://doi.org/10.5902/2179460Xxxxxx}
%
\submitionDate{xx/xx/xx}
%
\approvalDate{xx/xx/xx}
%
\publishDate{xx/xx/xx}
%
\yearonfooter{xxxx}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
\usepackage{pgfplots}
\usepackage{graphicx}

@@

\usepackage{booktabs}
\usepackage{multirow}

\usepackage{listings}
%
%----------------------------------------------------------------------------------------
%	YOUR CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\sisetup{math-micro=\text{µ},text-micro=µ}
%
\lstset{language=Fortran,
    basicstyle=\footnotesize\ttfamily,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\itshape,
    stringstyle=\itshape\color{magenta},
    numbers=left,
    numberstyle=\color{gray}\footnotesize\ttfamily,
    numbersep=9pt,
    showspaces=false,
    showstringspaces=false,
    breaklines=true,
    tabsize=4,
    frame=leftline,
    framerule=1pt,
    rulecolor=\color{cncolor},
    morekeywords={program, end, subroutine, end subroutine, if, then, else, endif, do, enddo, real, integer, logical, dimension, allocatable, intent, call}
}
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
\newcommand{\citeauthoryearpage}[2]{
  (\citeauthor{#1}, \citeyear{#1}, p. #2)
}
%
\newcommand{\citeapud}[3]{
  (\citeauthor{#1} {\it apud} \citeauthor{#2}, \citeyear{#2}, p. #3)
}

%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data Collection and Analysis}
%
\portugueseTitle{Explorando a Dinâmica dos Raios e seus Efeitos Térmicos: Insights a partir da Coleta e Análise de Dados}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{I},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{I},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{II},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Laboratory 84, Kensal Green University, No 23003, Harrow Road, Queens Park, London, UK}
  \affiliation{II}{Botafogo Departament, São João Batista University, Rio de Janeiro City, RJ, Brazil}
}

\shortHeaderTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data ...}
\shortHeaderAuthors{Babbage{\it~et~al.}}
%
\portugueseAbstract{
Os relâmpagos, um fenômeno natural poderoso, não só despertam nossa curiosidade, mas também têm um impacto significativo no ambiente circundante. Este estudo tem como objetivo investigar a dinâmica dos relâmpagos e seus efeitos térmicos por meio de uma análise abrangente de dados coletados pelo Electroplumbus Nimbodetector, em conjunto com o veículo voador 14-Bis. A configuração experimental oferece uma plataforma única para a coleta de dados em tempo real dentro de tempestades de raios, permitindo a exploração dos processos intricados associados às descargas de raios e aos fenômenos térmicos resultantes. A correlação entre a intensidade dos raios e a transferência de radiação térmica é examinada por meio de uma série de experimentos de campo e medições. Os resultados revelam uma relação significativa, com um aumento na energia transferida por radiação correspondendo a raios de maior intensidade. Ao estudar as transições atômicas subjacentes dentro do detector, são obtidos insights sobre a conversão da energia dos relâmpagos em calor no ar circundante. Essas descobertas contribuem para nossa compreensão dos fenômenos térmicos induzidos por relâmpagos e lançam as bases para pesquisas adicionais em ciências atmosféricas, meteorologia e estudos ambientais. As implicações deste estudo se estendem a medidas de segurança aprimoradas, ciência climática e conhecimento aprofundado da dinâmica atmosférica.
}
%
\portugueseKeywords{Raio; Radiação; Experimento Aéreo; Tempestade}
%
\englishAbstract{
Lightning, a powerful natural phenomenon, not only captivates our curiosity but also significantly impacts the surrounding environment. This study aims to investigate the dynamics of lightning and its thermal effects through a comprehensive analysis of data collected by the Electroplumbus Nimbodetector, in conjunction with the 14-Bis flying vehicle. The experimental setup provides a unique platform for real-time data collection within lightning storms, allowing for the exploration of the intricate processes associated with lightning discharges and the resulting thermal phenomena. The correlation between the intensity of lightning strikes and the transfer of thermal radiation is examined through a series of field experiments and measurements. The results reveal a significant relationship, with an increase in the energy transferred by radiation corresponding to higher intensity lightning strikes. By studying the underlying atomic transitions within the detector, insights into the conversion of lightning energy into heat in the surrounding air are gained. These findings contribute to our understanding of lightning-induced thermal phenomena and lay the foundation for further research in atmospheric science, meteorology, and environmental studies. The implications of this study extend to improved safety measures, climate science, and enhanced knowledge of atmospheric dynamics.
}
%
\englishKeywords{Lightning; Radiation; Airborne experiment; Storm}
%
%----------------------------------------------------------------------------------------
\begin{document}

@@

\section{Introduction}
%
Lightning, a powerful natural phenomenon, has long fascinated scientists and researchers due to its immense energy and unpredictable behavior. The study of lightning and its effects on the surrounding environment is crucial for gaining a deeper understanding of atmospheric dynamics and improving safety measures against its potential hazards. In particular, the transfer of thermal radiation during lightning strikes plays a significant role in shaping the thermal characteristics of the atmosphere and has far-reaching implications for meteorology, climate science, and environmental studies.\par
%
\longquotation{Two difficulties are encountered in studying radiation within absorbing, emitting, and scattering media that make these studies, to say the least, challenging. First, absorption and emission of energy are occurring not only at system boundaries, but at every local point within the medium [...]. A second difficulty is that spectral effects are often much more pronounced in gases than for solid surfaces. \citeauthoryearpage{Siegel1968}{2}}
%
To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required. In this paper, we present the results of a comprehensive study conducted using the 14-Bis flying vehicle and the Electroplumbus Nimbodetector, designed specifically for data collection within lightning storms. These innovative instruments enable researchers to gather valuable insights into the intricate processes associated with lightning discharges and the resulting thermal phenomena.\par
%
In the following sections, we present the experimental setup, data collection methods, and data analysis techniques employed in this study. Subsequently, we discuss the results obtained, highlighting the correlation between lightning strikes and the transfer of thermal radiation. Finally, we conclude with a summary of the findings, their significance, and future research directions.\par
%
\section{Experimental Setup}
\subsection{The 14-Bis flying vehicle}
The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms. The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions \citeapud{Pimenta1987}{Torrens1992}{46}.
%
\begin{figure}[!h]
  \caption{The 14-bis flying vehicle}
  \vspace{-3mm} 
  \begin{center}
    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
  \end{center}
  {\footnotesize
  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}\\
  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons}
    \label{fig:triangle2}
\end{figure}
%
Its streamlined shape is optimized for aerodynamic efficiency, minimizing drag and turbulence to facilitate smooth movement through the air. The veicle incorporates pairs of rigid horizontal structures projecting from both sides, designed to provide stability and support during flight \citep{Wipo}, enabling the driver to maintain control even in the presence of strong winds and atmospheric disturbances.\par
%
Within the open cockpit, the driver securely straps into a harness, ready to embark on their mission into lightning storms. The propulsion system powered by the kerosene motor generates the necessary thrust for controlled ascent \citep{Torrens1992}, while the open design ensures an immersive experience for the driver, allowing them to observe and collect data in real-time.\par
%
With its purpose-driven design and reliable motor, the 14-Bis flying vehicle represents an instrumental tool for conducting data collection within lightning storms. The combination of an open cockpit, sturdy structural elements, and efficient propulsion system allows for precise maneuverability and enables researchers to gather valuable insights into the dynamics of these atmospheric phenomena.
%

@@

  The 4th generation Electroplumbus Nimbodetector is a specialized device designed to collect data from a sensor and measure thermal radiation during lightning strikes. The device incorporates a modified version of the Plumbus Combobulator in its core, along with a specially engineered sensor that has a prism shape and is filled with an enriched Glowing Schleem substance. The purpose of the device is to gather data on lightning discharges and study their effects on the surrounding air.\par
  %
  The sensor within the Electroplumbus Nimbodetector is designed to capture thermal radiation emitted during lightning strikes. When a lightning event occurs, the Glowing Schleem inside the prism-shaped sensor heats up. Due to the low heat capacity of the Schleem, the temperature rise is rapidly measured, providing instant data on the thermal effects of the lightning discharge.\par
  %
  To determine the temperature of the air surrounding the sensor, the Plumbus Combobulator within the device incorporates a conventional thermometer with hight heat capaciity. The thermometer is strategically strategically positioned on the rear of the 14-bis flying vehicle to measure the air temperature in the vicinity of the sensor. By comparing the temperature of the Schleem-filled sensor and the air temperature measured by the thermometer, we can establish the temperature difference, which is crucial in assessing the impact of the lightning strikes' radiation on the surrounding air.\par
  %
  The Electroplumbus Nimbodetector undergoes rigorous calibration and validation processes to ensure accurate and reliable measurements. Prior to deployment, the device is calibrated against reference instruments and tested under controlled laboratory conditions to establish its performance characteristics. Special attention is given to the sensitivity, precision, and response time of the sensor and thermometer to ensure the accurate capture of data during lightning strikes.
  %
  \begin{figure}[!h]
    \newcommand\x{0.25}
    \caption{The 4th generation of the Electroplumbus Nimbodetector}
    \begin{center}
      \vspace{-3mm}
      \begin{minipage}[t]{\x\linewidth}
        \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
        \captionsetup{justification=centering, font=footnotesize}
        \caption*{(a)}\label{fig:triangle2a}
      \end{minipage}
      \begin{minipage}[t]{\x\linewidth}
        \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
        \captionsetup{justification=centering, font=footnotesize}
        \caption*{(b)}\label{fig:triangle2b}
      \end{minipage}\\
    \end{center}%
    \vspace{-1mm}
    {\footnotesize
    Source: Craiyon website, see \citep{Craiyon}\\
    Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance\\
    }
    \label{fig:triangle2}
    \end{figure}\vspace{-10mm}
  %
  \subsection{Data Collection}

@@

\section{Results and Discussion}

@@

The chart presents the number of lightning strikes detected by the Nimbus Detector within different altitude ranges. As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.\par
%
The chart presented in Figure 1 illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation. As the intensity of the lightning strike increases, there is a clear upward trend in the energy transferred. This observation supports the hypothesis that lightning strikes contribute to an enhanced transfer of thermal radiation to the surrounding air.\par
%
The strong correlation observed between lightning strikes and the energy transferred by radiation reinforces the reliability of the data collected by the Electroplumbus Nimbodetector. These findings provide valuable insights into the thermal dynamics associated with lightning discharges and contribute to a better understanding of the effects of lightning on the surrounding environment.\par
%
Moreover, it is important to note that light alone cannot directly heat gas molecules. Instead, during a lightning strike, the light emitted excites the electrons in atoms within the detector. These atoms are already vibrating at a certain frequency. Some of these atoms vibrate with sufficient vigor that their vibrational energy matches the electronic energy (photons) absorbed from the lightning, effectively reaching resonance with the solar energy. As a result, these atoms undergo a quantum transition from being "electronically excited" to "vibrationally excited," causing the entire atom to move. The surrounding air perceives this excited vibration as "heat."\par
%
This mechanism provides a deeper understanding of how the energy from a lightning strike is converted into thermal energy in the air. By studying the vibrational and electronic transitions occurring within the atoms of the detector, we can further elucidate the intricate processes involved in the thermal effects of lightning discharges.\par
%
In conclusion, this study demonstrates a strong correlation between the intensity of lightning strikes and the transfer of thermal radiation. The data collected by the Electroplumbus Nimbodetector, along with the presented chart, provides robust evidence supporting this relationship. Additionally, the exploration of the underlying processes involving electronic and vibrational transitions within the detector atoms enhances our comprehension of how lightning energy is converted into heat in the surrounding air. These findings contribute to the scientific understanding of lightning-induced thermal phenomena and lay the foundation for future research in this field.

\section*{Acknowledgements}

We gratefully acknowledge the Lupus Institute for their financial support, which has made this work possible. Also, we want to express our sincere appreciation to the open.ai for its invaluable assistance in the development of this fictional scientific paper.

@@

\theauthorcontributions

\howtocite

\section*{Appendix}
\lstinputlisting[caption=Foobar program, label={lst:listing-f90}, language=Fortran]{foobar.f90}
